\subsection{Silicon Pixel Detector\label{subsec:SiPixel}}
A new silicon pixel detector including 4 layers is being installed and commissioned. The detector FE electronics and
sensors is equivalent to the legacy detector while the whole off detector electronics was redesigned and based on the
latest FPGA technology (Xilinx virtex-7 family). The new firmware designs takes already into account high multiplicity
events. However, at present the performance of the latter has not been evaluated in HI multiplicity environment. An
electronics board with the scope to emulate the detector response was also designed to perform the commissioning of the
off detector electronics. The pixel group toke the responsibility to use this latter and define as soon as possible the
pixel operational parameters. A person in the HI group should however act a liaison person and provide the necessary
information required by the pixel group to perform the emulation. Accordingly, also the results should be evaluated and
possible solutions identified in case the performances are below expectations. As a rough estimation, a couple of months
should be enough for this activity.


\subsection{Silicon Strip Tracker\label{subsec:SiTracker}}
In standard p-p collision operation, the tracker detector sends the full detector information to 439 Front End devices
(FEDs). They apply the common mode noise subtraction and the strip zero suppression. However the common noise
subtraction algorithm implemented in the tracker FEDs firmware doesn’t allow compensation of the baseline distortion
observed in high multiplicity HI events. The solution adopted up to now was to bypass the tracker zero suppression in
the tracker FEDs and implement a specific HI common mode noise subtraction and zero suppression algorithms as a HLT
process. However, this solution implies and heavy load on the link between the FEDs and the DAQ.  The whole
interconnection was indeed designed with a maximum of ~ 400 MB/s per FED (two links of 200 MB/s each for heavy load
FEDs).  Considering that in average fragment size it is at ~32 kB/event. The readout limit is at around 12 kHz. It was
also already demonstrated that the FED is designed to sustain up to 520 MB/s. In this optic the only solutions available
are either to increase the number of links between the tracker FEDs and the DAQ or to reduce the data payload. The first
solution appear to be too complicated adding other ~400 links. Apart the technical constraints, there would also not be
enough time to install and commission the links during the EYTS. The second option is to reduce the data payload. A FED
firmware version implemented already in 2015 allows the reduction from 10 to 8 the number of bits readout by each strip
ADC. However, this strategy would allow moderate increase of < 20 % of the overall L1 rate at the cost of a reduction of
the detector resolution/sensitivity. At present there are not conclusive studies on the effects of this change on the
overall tracking efficiency. The second strategy considered is to modify the FEDs firmware including a more refined
common mode subtraction algorithm accounting for baseline distortion.  At present this strategy is considered to be the
preferable considering the rate increase obtained. The system could run at > 50 kHz. The tracker FEDs are based on
Xilinx Virtex-2 FPGA that is quite limited in term of on chip resources as well as clock frequency. This limitation
implies that only algorithm designed with specific attention could be implemented in the FEDs FPGA. It also implies that
the FED firmware development should be branched between p-p and Pb-Pb operation not having enough on-chip resources to
maintain both features. In 2013 a specific HI zero suppression algorithm designed for high multiplicity environment and
that would satisfy the FPGA constraints was designed offline and it is named “baseline follower”.  Preliminary studies
performed by the tracker and HI groups showed promising performance results for the algorithm. The first part of the
project requires the detailed study of the algorithm offline. It will imply roughly 3 months of work and detailed
clustering and tracking studies. Hardware feasibility studies are going to be performed in parallel by tracker
engineers. During this phase the HI group should participate in providing the required information but the amount of
work could not be quantified yet. In the late spring/early summer 2017 the project will be handed over completely to the
HI group where a developer will implement the actual algorithm in firmware. We estimate that the activity of coding will
last between 6 and 8 months. Afterwards, three months commissioning time including tests on the bench and test at P5
should be considered. This schedule should leave some resources available for the actual 2018 HI run preparation. At
present the tracker group is focusing on the tracker operation during p-p collisions and the tracker upgrade project. In
this optic, a significant fraction of the work required for this project will need to fall under the HI group
responsibility as mentioned above. 
