\subsection{L1 trigger\label{subsec:L1Trigger}}
For the 2015 Pb-Pb run an upgraded L1 trigger system was designed. The Stage-1 L1 trigger was operated with specific HI algorithms. However, in the middle of 2016 the full trigger upgrade (referred as Stage-2 in previous proposals) was installed and commissioned. The upgraded trigger system has a new layer-1 and the single MP7 board layer-2 was replaced with 9 MP7 boards operating with a time-multiplexed architecture. Also the firmware was completely redesigned by the L1 team including a series of new algorithm specific to p-p collision operation. 

In this optics, it is mandatory for the 2018 HI run to port to the new system the specific HI algorithm. In the list we have a specific background subtraction, centrality triggers, single-track triggers and Q2 triggers. It was agreed with the L1 team that the stage-2 engineers would take care of the firmware implementation and commissioning. However, it will be responsibility of the HI group to provide support. It includes the performance studies of the algorithms and a specific description of the implementation. Furthermore some of the several tests on the bench or at P5 will be performed by the HI group. Also the compilation of the L1 and HLT menus will remain responsibility of the HI group. In term of manpower, it should be considered a person for 6 months to follow the implementation process of the layer-2 and uGT firmware as well as performing the performance studies needed for the algorithm implementation. The preparation of the L1 menu will take several months and it should not be considered as part of this time. 
