\subsection{Silicon Strip Tracker\label{subsec:SiTracker}} 
In standard p-p collision operation, the tracker detector sends the full detector information to 430 Front-End Driver (FEDs). 
They apply common mode noise subtraction and strip zero-suppression. However, the common noise subtraction algorithm implemented in the Tracker FEDs firmware doesn't allow
compensation of the baseline distortion observed in the presence of Highly Ionizing Particles (HIP), with the consequent
potential loss of clusters associated with the affected readout chip. Due to the stringent requirements on tracking for
high multiplicity HI events, the cluster-finding inefficiency propagates directly to the track-finding inefficiency,
depending on the centrality of the collision.

The solution adopted up to now was to bypass the tracker zero-suppression implemented in the tracker FEDs and send the
full detector information to the DAQ/HLT. HI-specific common mode noise subtraction and zero-suppression algorithms were
implemented as HLT processes. However, this solution results in a heavy load on the links between the FEDs and the DAQ
and on the DAQ itself. The links are based on S-Link technology with a maximum speed of 200 MB/s. Some FEDs (connected
to sensors in which higher multiplicity is expected) have duplicate links, allowing a maximum of $\sim 400$ MB/s per
FED.  Considering that on the average fragment size is ~32 kB/event, the readout limit is at around 12 kHz. It has
already been demonstrated that the FED itself is designed to sustain up to 520 MB/s of throughput. The limitation is
then only coming from the links to the DAQ.

In agreement with the Tracker group, the only solution available to significantly increase the overall L1 rate is to
modify the FEDs firmware either including a new zero suppression algorithm or adjusting the data content sent to the DAQ. 

In 2013 a specific HI zero-suppression algorithm designed for high multiplicity environments that would satisfy the FPGA
constraints was designed offline; it is named a ``baseline follower''. Perf  

For completeness, we should also report that other possible strategies were studied/considered to increase the L1 rate
without modifying the tracker FED FW. However, they were rejected as being either too complicated to be implemented or
as underperforming. The two other solutions envisaged were either to increase the number of links between the tracker
FEDs and the DAQ or to reduce the data payload. The first solution appears to be too complicated, adding an extra $\sim
400$ links. Apart from the technical constraints, there would also not be enough time to install and commission the
links during the available shutdown time. The second solution is to reduce the data payload. A FED firmware version
implemented already in 2015 allows the reduction from 10 to 8 in the number of bits read out by each strip ADC. However,
this strategy would allow only a moderate increase of $\le 20 \%$ of the overall L1 rate at the cost of a reduction of
the detector resolution/sensitivity. 
