\section{Budget}
\label{sec:funding}

In this proposal the overall budget for the MIT Heavy Ion Group contribution to the projects includes only the costs of manpower for the study, development and commissioning of the tracker FEDs firmware. Manpower for 2018 Pb-Pb run preparations will be a part of the activities covered by the CMS "Experimental Physics Responsibility" system that requires each CMS member to contribute to the service work, and is only mentioned here to provide context for the proposed activities. 

The full chain of development, testing and commissioning of Tracker FW will happen at CERN. The test facilities in CERN B906 and B186 will be used in the early phases while the production system will be used for the final commissioning. The interaction with the hardware and the experienced developer is vital for the project. This is why the group of people involved must be stationed at CERN in Geneva.

The members of the team from the heavy-ion groups will consist of a temporary firmware development engineer at CERN. The engineer will devote 12 months at 100 \% effort to the project starting June 2017. 
 
The cost of an engineer to be hired as temporary help at CERN is estimated at roughly 7000 CHF/month. 

%The costs is summarized in Table~\ref{OpCost} and they all include MIT overhead. 

%\begin{table}[hbt]
%\begin{center}
%\begin{tabular}{|c|r|r|r|r|r|}
%\hline
% 
%                &  \textbf{Research Scientist}  & \textbf{COLA}  & \textbf{Engineer} & \textbf{Travel}      &  \textbf{Total}\\
%                &  \textbf{at 50 \% effort (\$)}  & \textbf{(\$)}  & \textbf{(\$)} & \textbf{(\$)}      &  \textbf{(\$)}\\ \hline
%FY17            &              &        &          &           &         \\
%6/1/17-10/31/17  & 20,715      & 7,591  &  30,009  & 685       &  65,000    \\\hline
%FY18             &              &        &          &           &         \\
%11/1/17-10/31/18  & 51,057    & 18,219   &  50,412     &  312 & 120,000   \\\hline
%\textbf{Total}  & \textbf{71,772}    & \textbf{25,810}   &  \textbf{86,421}     &  \textbf{997} & \textbf{185,000} \\\hline
%\end{tabular}
%\end{center}
%\caption{L1 trigger rate upgrade for the 2018 HI Run funding profile, in \$}
%\label{OpCost}
%\end{table}
